Backpropagating Gravitational wave events

### 2022-03-14 src/ms.tex
Add paragraphs

In this work we showcase the power of the proposed method with two events, GW150914 and GW191129.
We show the joint posterior of the two events' progenitor parameters and hyper-parameters.
In particular, to the authors knowledge, this is the first time the correlation between progenitor parameters and hyper-parameters is shown.
Our work is not only a more efficient way to study GW events' progenitors,
but also allows the possibility of measuring the astrophysics related the binary evolution.

@@

We hope this letter would motivate the community to build the relevant infrastructure mentioned above,
so in the near future we can explore the full parameter space of binary evolution models with the next-generation GW detectors network.

>>>>

In this work we showcase the power of the proposed method with two events, GW150914 and GW191129.
We show the joint posterior of the two events' progenitor parameters and hyper-parameters.
In particular, to the authors knowledge, this is the first time the correlation between progenitor parameters and hyper-parameters is shown.
Our work is not only a more efficient way to study GW events' progenitors,
but also allows the possibility of measuring the astrophysics related the binary evolution, especially in capturing the correlation between different hyper-parameters.

@@

To summarize, we propose a novel method to recover the posterior samples in the evolutionary parameter space for each GW event.
We "back propagate" the posterior in the observable space to the evolutionary parameter space,
thus allowing us to study the correlation between progenitor parameters and hyper-parameters.
We demonstrate the capability of this method with two events, GW150914 and GW191129, while employing the binary population synthesis model \texttt{COSMIC}.
We 
We hope this letter would motivate the community to build the relevant infrastructure mentioned above,
so in the near future we can explore the full parameter space of binary evolution models with the next-generation GW detectors network.
